\plaintitle

### 2021-01-16 draft.tex
Changes on "Discussion" - Dragos

Upon finishing their report about their own experience, each researcher had to take a picture of their current study environment (see Figure~\ref{fig:figure1} as an example) and attach it to the report. Afterwards all reports where analysed by each researcher and the  researcher-participant had to perform a presentation of their experience to all other researchers. Later on, the information was analysed using \emph{thematic analysis} within \emph{Miro}\footnote{\url{https://miro.com/}} so as to extract possible interview questions for later use. After having decided on the possible interview questions, a sample semi-structured interview took place, having one of the researchers as a participant, and two others as interviewer and observer. Upon finishing the sample interview, the interview questions had been filtered to only five central ones in order to be used as a guide for the incoming participant interviews.
\begin{figure}
\centering
  \includegraphics[width=1\columnwidth]{figures/auto-e-picture}
  \caption{Sample picture from the Auto-Ethnographic method, showing the desk of one of the researchers}~\label{fig:figure1}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=1\columnwidth]{figures/perfect-setup}
  \caption{A sample photo from the Photographic Ethnography method given by one of the participants, it is the desired "perfect study environment''}~\label{fig:figure2}
\end{figure}

@@

The analyze of the photos received from the participants and from the researchers involved in the study, showed unique, personalized study environments,  with a commune focus on ergonomics, efficiency and aesthetics. The result showed that the position of the working desk is usually located close to a direct source of natural light.  The importance of a natural source of light was mentioned by several participants during the semi-structured online interview process. Items such as: second screen, laptop, lamp, plants, notebooks were …

@@

Things to talk about: 
1.Universities could open libraries or study spaces. Even increase the amount of space post-pandemic, as an issue already existed
2. Items that are we recommend to use for study and the uni should give discounts to
3.

\subsection{Biases in participation}
There was an obvious variation in the result we achieved. It is therefore feasible to discuss what the research results would have looked like if the number of participants had been higher, or if the participants had studied another educational discipline than engineering. All the participants were students at the Vienna University of Technology in Austria which is a delimitation. Anyway, we believe it was an decent variety of life situations among these participants and thus a representative research overview.

@@

However, we argue that unaware biases could still affect the participants behavior and our own interpretations because we knew these students before the research.

@@

\subsection{Ergonomics and comfort}
Studying in the home office sets a new level of understanding ergonomics depending on the basic office equipment. We would like to point out that there was dissatisfaction with the participants' office chairs, which they considered to be unergonomic in many various aspects. The chair was described as stiff, offered a bad working posture and could not be adjusted in height. Hence, it was not an office chair but a normal chair. We therefore claim that there may be negative effects in the back, neck and shoulder if students do not choose to upgrade their chair in the future home office. Studying at the university offers better ergonomics with chairs, benches and lamps that are adapted for university studies. Consequently, five of the participants answered that they wanted to upgrade their chair if they could. Three of the participants also answered that they would prefer to have a separate office if they could, which is not possible without moving into a new living accommodation. We therefore believe that it is necessary for all students to reflect our their own situation and be flexible and creative in how they can improve their own home office. All students may need different solutions as situations always differ. We also believe that inappropriate routines that office equipment can generate are difficult to detect. It is easy to get used to equipment that works but is not optimal. We therefore urge all students to reflect about their home office standard and how it could be improved. We consider it is important to ask the question "what do I need to improve if I am going to study here for a year?". According to the research findings, all participants received some form of negative ergonomics aspect that affected the participants’ studies. Working light, fresh air or working posture were the some main problems. Even sitting still in one and the same room was considered as a problem. Improving the study area as early as possible, we claim will prevent discovered and undiscovered problems. We base this discussion on the fact that the participants had difficulty answering questions about their perfect study setup. We thus argue that the participants had not processed their own thoughts about whether they could improve their home office or not, which indicates that ergonomics have been prioritized away in the noise of distance studies and other undiscovered problems. This can, for example, be related to the general student's financial limitations. One of the participants also pointed out that his eyes ached in the evening, after hours in front of the computer. But this can be avoided with regular breaks or blue light-repellent glasses, which is also an indication that the student does not know how to improve their ergonomics. We believe that this is not because the student does not want to improve his health, but because the student don not prioritize the time of reflecting about the home office setup. We would therefore like to encourage all higher education institutions as well as students to investigate the research that today exists on how to improve ergonomics in the home office.

\subsection{Limitations}

@@

\section{Acknowledgments}
Thank you to all our interview participants for taking their time off their studies and work in order to help us with this assignment. Thank you to TU Wien for giving us access to the needed tools in order to prepare the assignment,  \textit{as good as they are}. No other funding was provided.

>>>>

Upon finishing their report about their own experience, each researcher had to take a picture of their current study environment (see Figure~\ref{fig:figure1} as an example) and attach it to the report. Afterwards all reports where analysed by each researcher and the  researcher-participant had to perform a presentation of their experience to all other researchers. Later on, the information was analysed using \emph{thematic analysis} within \emph{Miro}\footnote{\url{https://miro.com/}} so as to extract possible interview questions for later use. After having decided on the possible interview questions, a sample semi-structured interview took place, having one of the researchers as a participant, and two others as interviewer and observer. Upon finishing the sample interview, the interview questions had been filtered to only five central ones in order to be used as a guide for the incoming participant interviews.
\begin{figure}
\centering
  \includegraphics[width=1\columnwidth]{figures/auto-ethnography.JPG}
  \caption{Sample picture from the Auto-Ethnographic method, showing the desk of one of the researchers}~\label{fig:figure1}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\columnwidth]{figures/auto-ethnography-annotated.JPG}
  \caption{The same sample picture from the Auto-Ethnographic method, now annotated with small comments from Miro}~\label{fig:figure2}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=1\columnwidth]{figures/perfect-setup}
  \caption{A sample photo from the Photographic Ethnography method given by one of the participants, it is the desired "perfect study environment''}~\label{fig:figure3}
\end{figure}

@@

The analyze of the photos received from the participants and from the researchers involved in the study, showed unique, personalized study environments,  with a commune focus on ergonomics, efficiency and aesthetics. For a better understanding of the students environment, the photo sent by the participants were used as a complementary visualization for the description given in the semi-structured interviews. The result showed that the position of the working desk is usually located close to a direct source of natural light. The importance of a natural source of light was mentioned by several participants during the semi-structured online interview process. Items such as: second screen, laptop, lamp, plants, notebooks were founded present in most of the study setups. The participants explained that the use of a second screen can improve productivity as you can easily multitask when required. When asked about an improvement they would made to the actual setup, participants that were not possessing any additional display mentioned the benefits they would get from owning one.

@@

\subsection{Biases in participation}
There was an obvious variation in the result we achieved. It is therefore feasible to discuss what the research results would have looked like if the number of participants had been higher, or if the participants had studied another educational discipline than engineering. All the participants were students at the Vienna University of Technology in Austria which is a delimitation. Anyway, we believe it was an decent variety of life situations among these participants and thus a representative research overview.
Upon a closer look within the participant’s characteristic, it must be noted that our “sample” is not very diverse from a geographical point of view. All participants, including the researchers themselves live and study either in Austria or another EU member country. In terms of degree, only Bachelors, Masters and PhD students have participated, no lower education. The degree’s have been mostly IT related and both from TU Wien and other European universities as well as Erasmus students

@@

However, we argue that unaware biases could still affect the participants behavior and our own interpretations because we knew these students before the research.
A very important bias that had occurred within our interviews is due to the already existing relationships between the researchers and the interview participants as well as the decision of not utilizing the classical interviewer/observer technique due to time constraints as well as the avoidance of causing discomfort towards the participants due to talking about their lives with an unknown person in the interview.

@@

\subsection{Health and comfort}
Studying in the home office sets a new level of understanding ergonomics depending on the basic office equipment. We would like to point out that there was dissatisfaction with the participants' office chairs, which most have described as being "unergonomic''. The chairs were described as stiff, offered a bad working posture and could not be adjusted in height. We therefore claim that there might be persistent health issues if students do not choose to upgrade their chair in the future home office. Studying at the university offers better ergonomics with chairs, benches and lamps that are adapted for university studies. Consequently, five of the participants answered that they wanted to upgrade their chair if they could. Three of the participants also answered that they would prefer to have a separate office if they could, which is not possible without moving into a new living accommodation. We therefore believe that it is necessary for all students to reflect on their own situation and be flexible and creative in how they can improve their own home office. All students may need different solutions as situations always differ. We also believe that inappropriate routines that office equipment can generate are difficult to detect. It is easy to get used to equipment that works but is not optimal. We therefore urge all students to reflect about their home office standard and how it could be improved. We consider it important to ask the question "what do I need to improve if I am going to study here for a year?". According to the research findings, all participants received some form of negative ergonomics aspect that affected their studies. Good lighting, fresh air or working posture have been the main problems detected. Sitting still in one and the same room was considered as a negative aspect of distance learning. Improving the study area as early as possible, we claim will prevent easy to avoid health issues in the long run.

One of the participants also pointed out that his eyes ached in the evening, after hours in front of the computer. But this can be avoided with regular breaks or blue light-repellent glasses, a solution that the participant did not think about. We believe that this is not because the student does not want to improve his health, but because the student does not prioritize the time of reflecting about the home office setup. We would therefore like to encourage all higher education institutions to offer students a sort of \emph{tips and tricks manual} based on existing research on ergonomics and other desk related comfort improvements in order to better prepare students towards distance learning and gather their attention on the matter.

\subsection{Financial Limitations}
From the fact that participants had difficulty answering questions about their perfect study setup, we argue that they had not processed their own thoughts about whether they could improve their home office or not, which indicates that ergonomics have been prioritized away in the hectic noise of distance learning as well financial limitations. While most of our participants also work, several do not, and one has actually had their job activity interrupted due to the ongoing pandemic restrictions. And so financial limitations have halted their desire of improving their work environment further. Possible partnerships between educational institutions and retailers in order to provide discounts for students could prove effective in cutting costs on behalf of the students and even boost sales for retails, providing a win-win solution. Another solution could be found from the already established furniture rental services, that currently work with other companies in facilitating their move within cities like Vienna, by starting to provide also low to mid end study equipment for Erasmus students.

@@

\section{Acknowledgments}
Thank you to all our interview participants for taking their time off their studies and work in order to help us with this assignment. Thank you to TU Wien for giving us access to the needed tools in order to prepare the assignment, and of course to our supervisory professors for offering us guidance along the way.
